% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\hyphenation{testing analytics management}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\usepackage{simplemargins}
\setleftmargin{0.5in}
\setrightmargin{2.0in}
\settopmargin{0.7in}
\setbottommargin{0.3in}


\usepackage{hyperref}
%\hyperref[mainlemma]{lemma \ref{mainlemma}}
\hypersetup{
    bookmarks=false,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in Acrobats bookmarks
    pdftoolbar=false,        % show Acrobats toolbar?
    pdfmenubar=true,        % show Acrobats menu?
    pdffitwindow=true,     % window fit to page when opened
    pdfnewwindow=true,      % links in new window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=blue           % color of external links
}

%\addtolength{\oddsidemargin}{-0.875in}
%\addtolength{\evensidemargin}{-0.875in}
%\addtolength{\textwidth}{1.5in}
%
%\addtolength{\topmargin}{-0.875in}
%\addtolength{\textheight}{1.5in}


\begin{document}

\name{Roberto Arias Ruiz}
% \address used twice to have two lines of address
%\address{Calle Laforja, 8. pral-1era, 08006. Barcelona, Espa\~{n}a}
\address{+34 678714822 / roberlamerma@gmail.com}

\begin{resume}
 
\section{PROFILE}       
                \begin{itemize}  \itemsep 2pt % reduce space between items
                \item Software Engineer with broad experience in Software 
                Development Life Cycle (analysis, design, maintenance and
                deployment of software) under several platforms/architectures.               
                \item Project management. Specialized in security solutions, as
                it is my field of expertise (Masters)
                \item Ability to cope with critical related processes and high 
                pressure situations.              
                \item Excellent communications skills (Spanish and English)
%                \item{\hskip-.25in\llap{1997}\hskip.25in{}worked here} 
%                \item{\hskip-.25in\llap{\parbox[b]{1in}{This is a longer note that might wrap}}\hskip.25in{}worked there}
                \end{itemize}
         
\section{EXPERIENCE \\ \footnotesize{(references available upon request)}}
                {\sl Senior Developer} \hfill April 2010 -- Now \\
                \textbf{Wolters Kluwer} 
                $<$\url{www.wolterskluwer.es}$>$ \hfill \textit{Barcelona, Spain}
                \begin{itemize}  \itemsep 2pt % reduce space between items
                \item Analysis, Development and Mainteinance of a development \textit{Framework} 
                in a joint project among all the European headquarters of the group.
                \item Coordination with a development team \textit{(outsourcing partner)} 
                in India.
                \item Use of SCRUM methodology, following a \textit{(Domain Driven Design)}, under
                TFS.
                \item .Net 4.0, C{\#}, SQL Server, Entity Framework, WCF, WPF, Silverlight.
                \\
                \end{itemize}
                
                {\sl Analyst} \hfill            March 2007 -- February 2010 \\
                \textbf{Knosos, Grupo Amper} 
                $<$\url{www.amper.es}$>$ \hfill \textit{Barcelona, Spain}
                \begin{itemize}  \itemsep 2pt % reduce space between items              
                \item Project bidding (documentation) according to IEEE/EIA 12207
                and ISO 9001.               
                \item Software engineering: Requirements, analysis \& design, 
                resource estimation, development, testing (Test Units, Benchmarking,
                Profiling) and maintenance of Software solutions. Versioning control
                and deployment strategies.               
                \item Strategy, design and implementation of services under ITIL 
                framework.               
                \item Design of .NET services and applications: client-server
                solutions, MVC, distributed applications, high availability.
                Technologies: WPF, WCF, Remoting, SOAP, Compact Framework,
                Sockets, etc.
                \item Research and Development of embedded systems and mobile
                applications.
                \\
                \end{itemize}


                {\sl Programmer Analyst} \hfill December 2005 -- January 2007 \\
                \textbf{Grupo 3C} 
                $<$\url{www.tresce.com}$>$ \hfill \textit{Barcelona, 
                Spain}
                \begin{itemize}  \itemsep 2pt % reduce space between items
                \item Apache and IIS tuning. Management of redundant and highly
                available platforms.
                \item Development of web applications: PHP, Perl. Technologies: HTML,
                CSS and Javascript. AJAX.
%                \item SEO: Indexing and PageRank. Knowledge of Google API and
%               indexing tools: Google Analytics, Google Sitemaps, Google API, etc.
                \\
                \end{itemize} 

                {\sl Freelance Programmer} \hfill August 2004 -- October 
                2005 \\
                \textbf{iChameleon Group INC} 
                $<$\url{www.ichameleongroup.com}$>$ \hfill \textit{Miami, USA}
                \begin{itemize}  \itemsep 2pt % reduce space between items
                \item Freelance project for the development (Frontend
                and Backend) of an online music shop. Perl, FastCGI, PostgreSQL.
                \item Direct management of the project with the client.
                \item Development of Mac (Apple) applications on Objective-C
                language, under Cocoa Framework.
                \\
                \end{itemize}
                
                \\
                \\

                {\sl Programmer (trainee)} \hfill August 2003 -- July 
                2004 \\
                \textbf{Gaiax Co, LTD} 
                $<$\url{www.gaiax.co.jp}$>$ \hfill \textit{Tokyo, 
                Japan}
                \begin{itemize}  \itemsep 2pt % reduce space between items
                \item Design and development of a game oriented web platform
                for the Japanese, using Perl (mod\_perl and FastCGI)
                \item Research project on high processing capacity 
                technologies. Benchmark and Profiling of Web applications.
                \\
                \end{itemize} 

%                {\sl System Administrator} \hfill October 1999 -- July 
%                2002 \\
%                \textbf{Computation Laboratory, USB} 
%                $<$\url{www.ldc.usb.ve}$>$
%                \hfill \textit{Caracas, Venezuela}
%                \begin{itemize}  \itemsep 2pt % reduce space between items
%                \item Design and maintenance of several nodes of the university 
%                LAN. Maintenance of all software.               
%                \end{itemize}

\section{ACHIEVEMENTS}   
                \begin{itemize}  \itemsep 2pt % reduce space between items
                \item Coordination of the team who in cooperation with EUROCONTROL
                (\url{www.eurocontrol.int}) designed and implemented the data
                protocol ASTERIX, used by several Homeland Security solutions 
                deployed by Amper, locally and in Europe.               
                \item Design and implementation of a data transport and transmission 
                protocol through SIRDEE network (Tetrapol)                
                \item Promoted the deployment of a structured methodology for issue
                tracking and knowledge management (Jira + Confluence. 
                \url{www.atlassian.com}), currently used by Knosos/Amper.
                \item Design, deployment and maintenance of networking servers and 
                services under multiple communication platforms: GPRS, Tetra, 
                TETRAPOL, Inmarsat, for Knosos/Amper.
                \item Successful management of the project that automatized 
                every process that dealt with real time information analysis, on 
                3C Formaci\'{o}n.                
                \item Improvement of positioning (SEO) and indexation (Google) of
                several web sites, on 3C Formaci\'{o}n.               
                \item Development and deployment of an online massive game
                (\url{sugolog.cafe.ocn.ne.jp}), which currently maintains
                a respectable popularity in the Japanense market.
                \item As System Administrator (LDC), I was part of the team that 
                developed the new topology of the university LAN, besides configuring
                and tuning all the network systems and processes.
                \item As a student, I was responsible for the laboratories 
                during my last two years at the University.
                \end{itemize}

\section{EDUCATION}
               \textbf{Master in IT Security,} \hfill October 2006 -- Agosto 2007 \\
               \textit{La Salle Foundation/ Ram\'{o}n Llull University} 
               \hfill Barcelona, Spain

               \textbf{Software Engineering,} \hfill 
               September 1997 -- July 2003 \\
               \textit{Sim\'{o}n Bol\'{i}var University} \hfill Caracas, Venezuela

%               \textbf{Primary \& High School,} \hfill October 1985 -- July 
%               1997 \\
%               \textit{Colegio San Ignacio de Loyola} \hfill Caracas, Venezuela

\section{COURSES}
               \begin{itemize}  \itemsep 2pt % reduce space between items
               \item \textbf{CCNA} Cisco: network desing, routing and 
               switching.
               \item \textbf{ITIL} Foundations Certification: management, 
               development, operations and IT services.
               \item \textbf{OPST} ISECOM: analysis and security testing methodologies.
               \item Advanced course on virtualization \textbf{VMWare} 
%               \item 3D animation and modeling course (\textbf{3D Studio Max})
               \end{itemize}

\section{LANGUAGES} 
               %\hfill 1: B\'{a}sico, 2: Regular, 3: Intermedio, 4: Experto, 
               %5: Materno \\ \\
               \textbf{English,}
               spoken, written and read: \textit{advanced}.
               \\
               \textbf{French,}
               spoken: \textit{basic}; written and read: 
               \textit{intermediate}.
               \\
               \textbf{Catalan,}
               spoken: \textit{basic}; written and read: 
               \textit{intermediate}.
               \\
               \textbf{Japanese,}
               spoken: \textit{basic}; written and read: 
               \textit{null}.
               \\
               \textbf{Spanish,}
               \textit{mother tongue}.
               
%\section{PROFESSIONAL \\AFFILIATIONS\\}
%               \begin{itemize}  \itemsep 2pt % reduce space between items
%               %\renewcommand{\labelitemi}{$\circ$}
%               \item \textit{ATI,} Asociaci\'{o}n de T\'{e}cnicos de Inform\'{a}tica \hfill Spain
%               \\
%               \\
%               \end{itemize}
 
\section{PERSONAL \\ DATA}  
               \textbf{Email:} \href{mailto:roberlamerma@gmail.com}{roberlamerma@gmail.com}\\
               \textbf{Address:} Calle Londres 25, 6to-1era, 08029. Barcelona, Espa\~{n}a\\
               \textbf{Phones:} 678714822 (mobile)\\
               \textbf{Salary expectations:} 35.000 EUR\\
               Drivers Licence\\
               Available to travel\\


\end{resume}
\end{document}







