\documentclass[line,margin]{res} 
\hyphenation{co-mmu-ni-ca-tion in-for-ma-tion auto-mated Roche Diagnostics}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\usepackage{simplemargins}
\usepackage{amssymb}

\setleftmargin{0.5in}
\setrightmargin{2.0in}
\settopmargin{0.7in}
\setbottommargin{0.3in}


\usepackage{hyperref}
%\hyperref[mainlemma]{lemma \ref{mainlemma}}
\hypersetup{
    bookmarks=false,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in Acrobats bookmarks
    pdftoolbar=false,        % show Acrobats toolbar?
    pdfmenubar=true,        % show Acrobats menu?
    pdffitwindow=true,     % window fit to page when opened
    pdfnewwindow=true,      % links in new window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=blue           % color of external links
}

\usepackage{graphicx} 

%\addtolength{\oddsidemargin}{-0.875in}
%\addtolength{\evensidemargin}{-0.875in}
%\addtolength{\textwidth}{1.5in}
%
%\addtolength{\topmargin}{-0.875in}
%\addtolength{\textheight}{1.5in}


\begin{document}

\name{Roberto Arias Ruiz}
\address{+34 678714822 / roberlamerma@gmail.com}

\begin{resume}
 
\section{PROFILE}       
                \begin{itemize}  \itemsep 2pt 
                \item Software Engineer with broad experience in all Software 
                Development Life Cycle milestones, under several platforms/architectures: Microsoft, Linux, MacOSX and emdedded devices.
                \item Scrum: expert on Agile methodologies. Effective leadership skills. Product and project vision.
                \item Ability to cope with critical related processes and high 
                pressure situations.              
                \item Excellent communications and presentation skills (Spanish and English)
                \end{itemize}
         

\section{EXPERIENCE \\ \footnotesize{(references available upon request)}}

                \textbf{Roche Diagnostics} 
                $<$\url{http://www.roche.com}$>$ \hfill May 2011 -- Now \\
                {\sl Product Owner} \hfill \textit{Sant Cugat, Spain}
                \begin{itemize}  \itemsep 2pt 
                \item Product owner for a Point of Care device that automates virus and disease detection using molecular (PCR) analysis.
                \item Work package (software Stories) creation and posterior acceptance for 2 teams on a distributed location setup (Spain and Switzerland)
                \item Requirements and usability (UX) engineering: analysis of high level requirements $\rightarrow$ creation of User Interface Sketches and 
                software Work Packages. Ensure requirement coverage and regression tests traceability using HP-ALM. Sketch creation using Balsamiq Mockups.
                \item Create roadmap and product vision, using proven Project Management artifacts.
                \item Coordination of external software providers.
                \end{itemize}

                {\sl Scrum {\&} Build Master / Senior Developer}
                \begin{itemize}  \itemsep 2pt 
                \item Coordination of a local 9 people Scrum team with several teams, 
                spread along Spain, India and Switzerland, for a major Laboratory Diagnostics project.
                \item .Net 4.5, C{\#}, TFS, Oracle/SQL Server, Entity Framework, WCF, WPF, Silverlight.
                \item Analysis of TFS Warehouse data (SQL and OLAP cubes). Creation of project management reports and KPI analysis, using Microsoft Reporting/Integration Services. 
                \\
                \end{itemize}
                

                {\sl Software Architect} \hfill April 2010 -- May 2011 \\
                \textbf{Wolters Kluwer} 
                $<$\url{http://www.wolterskluwer.es}$>$ \hfill \textit{Barcelona, Spain}
                \begin{itemize}  \itemsep 2pt 
                \item Analysis and Design for a core development \textit{Framework} 
                in a joint project among all the European headquarters of the group.
                \item Coordination with a development team \textit{(outsourcing partner)} 
                in India.
                \item Use of SCRUM methodology, following a \textit{Domain Driven Design}. .NET 4.5, C{\#}, WPF, WCF, TFS.
                \\
                \end{itemize}


                {\sl Senior Developer} \hfill            March 2007 -- February 2010 \\
                \textbf{Amper} 
                $<$\url{http://www.amper.es}$>$ \hfill \textit{Barcelona, Spain}
                \begin{itemize}  \itemsep 2pt         
                \item Project bidding (documentation) according to IEEE/EIA 12207
                and ISO 9001.               
                \item Software engineering: Requirements, analysis \& design, 
                resource estimation, development, testing (Test Units, Benchmarking,
                Profiling) and maintenance of Software solutions.               
                \item Design of .NET services and applications: client-server
                solutions, MVC, distributed applications, high availability.
                Technologies: WPF, WCF, Compact Framework,
                Sockets, etc.
                \item Research and Development of embedded systems and mobile
                applications.
                \\
                \end{itemize}


               {\sl Software Developer} \hfill December 2005 -- January 2007 \\
                \textbf{Grupo 3C} 
                $<$\url{http://www.tresce.com}$>$ \hfill \textit{Barcelona, 
                Spain}
                \begin{itemize}  \itemsep 2pt % reduce space between items
                \item Apache and IIS tuning. Management of redundant and high 
                traffic websites.
                \item Web development: PHP, Perl, MySQL. Technologies: HTML,
                CSS and Javascript. AJAX.
                \\
                \end{itemize} 

                {\sl Freelance Software Developer} \hfill August 2004 -- October 
                2005 \\
                \textbf{iChameleon Group INC} 
                $<$\url{http://www.ichameleongroup.com}$>$ \hfill \textit{Miami, USA}
                \begin{itemize}  \itemsep 2pt % reduce space between items
                \item Freelance project for the development (Frontend
                and Backend) of an online music shop. Perl, FastCGI, PostgreSQL.
                \item Development of Mac (Apple) applications on Objective-C
                language, under Cocoa Framework.
                \\
                \end{itemize}

               {\sl Software Developer (trainee)} \hfill August 2003 -- July 
                2004 \\
                \textbf{Gaiax Co, LTD} 
                $<$\url{http://www.gaiax.co.jp}$>$ \hfill \textit{Tokyo, 
                Japan}
                \begin{itemize}  \itemsep 2pt % reduce space between items
                \item Development of a game oriented web platform, 
                using Perl (mod\_perl and FastCGI)
                \item Research project on high processing capacity 
                technologies. Benchmark and Profiling of Web applications.
                \\
                \end{itemize} 

                {\sl System Administrator} \hfill October 1999 -- July 
                2002 \\
                \textbf{Computation Laboratory, USB} 
                $<$\url{http://www.ldc.usb.ve}$>$
                \hfill \textit{Caracas, Venezuela}
                \begin{itemize}  \itemsep 2pt % reduce space between items
                \item Design and maintenance of several nodes of the university 
                LAN. Maintenance of all software (Linux, Solaris) 
                \item Responsible for the admission of new members (initial exams, training, etc)              
                \end{itemize}

\section{ACHIEVEMENTS}   
                \begin{itemize}  \itemsep 2pt % reduce space between items
                \item Designed and lead the teams with the task of adding connectivity to the \href{https://www.cobasliat.com/}{\textsuperscript{\textregistered}Cobas \textsuperscript{\textregistered}Liat} Point of Care instrument, using custom messages and workflows based on the \textbf{POCT1-A} and \textbf{HL7} standards for exchange 
                 of medical information, at \href{http://www.roche.com}{Roche Diagnostics}.

                \item Succeded as the designated interface \textbf{(Product Owner)} between \href{http://www.roche.com}{Roche Diagnostics} and a external software contractor (Team of 10), 
                under a strict Scrum implementation where the contractor remuneration was based upon Scrum \textit{story points}.

                \item Improvement of \textbf{Continuous Integration} process on a 
                \href{http://www.roche.com}{Roche Diagnostics} major project: automated execution of test suites (unit, integration, regression) within Build Agents (\textbf{TFS}).
                \item Proposed and designed (team work) the architecture layers and modules for 
                all \href{http://www.roche.com}{Roche Diagnostics} internal \textbf{Reporting Solutions}
                (Project Management, KPI's, Monitoring, etc).
                \item Created the releasing process, including automated deployments, used to release \href{http://www.roche.com}{Roche Diagnostics} \textbf{Reporting Solutions}.
                \item In cooperation with \href{www.eurocontrol.int}{EUROCONTROL} 
                implemented the .NET and Java versions of the \textbf{data protocol} ASTERIX, used 
                by Homeland Security solutions developed by \href{http://www.amper.es}{Amper}.                             
                \item Design, deployment and maintenance of \textbf{networking servers} and 
                \textbf{services} under multiple communication platforms: GPRS, Tetra, 
                TETRAPOL, Inmarsat, for \href{http://www.amper.es}{Amper}.
                \item Delivery of a solution that succesfully automated (\textbf{Real Time})
                the processing of web information requests, at \href{http://www.tresce.com}{Grupo Tresce}.                
                \item Development and deployment of an \textbf{online massive game} at \href{http://www.gaiax.co.jp}{Gaiax Co, LTD}
                \item As System Administrator at \href{http://www.ldc.usb.ve}{LDC}, I was part of the team that 
                developed the new topology of the \textbf{university LAN}, besides configuring
                and tuning all the network systems and processes.
                \end{itemize}

\section{EDUCATION}
               \textbf{Masters on IT Security,} \hfill October 2006 -- Agosto 2007 \\
               \textit{La Salle Foundation/ Ram\'{o}n Llull University} 
               \hfill Barcelona, Spain

               \textbf{Software Engineering,} \hfill 
               September 1997 -- July 2003 \\
               \textit{Sim\'{o}n Bol\'{i}var University} \hfill Caracas, Venezuela

\section{COURSES \\ \footnotesize{(and certifications)}}
               \begin{itemize}  \itemsep 2pt % reduce space between items
               \item \textbf{CCNA} Cisco: network desing, routing and 
               switching. \textit{(renewal pending)}
               \item \textbf{Microsoft}: 496 - Administering Visual Studio Team Foundation Server 
               \item \textbf{ITIL} Foundations Certification: management, 
               development, operations and IT services.
               \item \textbf{OPST} (\href{http://www.isecom.org/certification/opst.html}{ISECOM}): analysis and security testing methodologies.
	    \item \textbf{CSM} (\href{https://www.scrumalliance.org/certifications/practitioners/certified-scrummaster-csm}{Scrum Alliance}): certified Scrum Master.
               \item \textbf{PSPO I} (\href{https://www.scrum.org/Assessments/Professional-Scrum-Product-Owner-Assessments}{SCRUM.org}): Professional SCRUM Product Owner.
	    \item \textbf{Game theory} online course at Standford university \href{https://www.coursera.org/course/gametheory}{via Coursera.org}. \textit{(with distinction)}
               \item Advanced course on virtualization using \textbf{VMWare} 
%               \item 3D animation and modeling course (\textbf{3D Studio Max})
               \end{itemize}


\section{LANGUAGES} 
               \textbf{English,}
               spoken, written and read: \textit{advanced}.
               \\
               \textbf{German,}
               \textit{(completed A2.2 level)}.
               \\
               \textbf{French,}
               spoken: \textit{basic}; written and read: 
               \textit{intermediate}.
               \\
               \textbf{Japanese,}
               spoken: \textit{basic}; written and read: 
               \textit{very basic}.
               \\
               \textbf{Spanish,}
               \textit{mother tongue}.

 
\section{PERSONAL \\ DATA}  
               \textbf{Email:} \href{mailto:roberlamerma@gmail.com}{roberlamerma@gmail.com} - \textbf{Phone:} 678714822 (mobile)\\
               \textbf{Address:} Calle Mercedes 8, Bajos-2da, 08024, Barcelona, Espa\~{n}a\\
               

\end{resume}
\end{document}







